---
title: "Rscript_template"
author: "..."
date: "2025-10-01"
always_allow_html: true
output:
  rmarkdown::github_document: default
  always_allow_html: default
  output:
  md_document:
    variant: gfm
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../") })
---

# Template File (Heading 1)
## the YAML header works with the default structure... (Heading 2)
- this template uses git-flavored markdown (gfm)...
- and is set to render to the parent directory...
- So you end up with *clean* markdown files for viewers
- with scripts,data, etc... in the other folders. 

## Required CHUNK for markdown rendering
```{r setup, include=FALSE}
base_dir <- "../" # output goes "up" into the containing folder (base dir)
base_url <- "" # keep as is - only needed if for html output/github pages versions (see readme and other templates
fig_path <- "../_plot_images/" # where image output should go

knitr::opts_knit$set(base.dir = base_dir)
knitr::opts_chunk$set(fig.path = fig_path,
                      cache.path = '../_cache/',  #log files go here - IF YOU ARE USING CACHE
                      # Some reproducible examples will want this FALSE/EXLCUDED so there isn't any 'hidden (cached) data' making it's way into your analysis/scripts. 
                      message=FALSE, warning=FALSE,
                      cache = FALSE) # set to TRUE if you want to use caching
```  

If you are maintaining the SAME setup for each of your script files, you can set the following parameters by SOURCEing the utility_functions.R script in this folder, and running the following function, OR SOURCING the default version directly, as seen below. 
```{r}
source("_templates/utility_functions.R") #loads the function but DOES NOT RUN IT
# you can then set invidiual arguments. 

source("default_slick_knit_ops.R") # runs the function with default arguments, output set to FALSE
```



## Note on Rmardkown or "Notebooks"
- This is an Rmarkdown, which allows code 'chunks' or 'blocks' and text in the same document.
- Code output - such as viewing tables or charts appears below blocks when you write them. 

- It is useful to write outlines and sections for specific chunks.
- And to write analytic notes below different code chunks. 
- The output of an Rmarkdown (.Rmd) can be published as a .PDF, word doc, or .HTML file. 

- In the YAML header and chunk above, are specific options for file organization.
  - Markdown documents -- readable versions of the analysis live in the main folder
  - The scripts that create these live in _Rscripts
  - *input* data in _data, including created data for analysis (e.g. R.data objects...)
  - *output* goes into _tables or plots_images depending on type.
